---
title: "Presentation in R Markdown"
author: "Andrea Puggioni"
date: "5/2/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## My new slide
Some content

## My title

- Bullet one
- Bullet two

1. Item a
2. Item b

### A top level subheading

#### A second level subheading


## My text

Plain  text

*italic*

**Bold**

`for (i %in% 1 : 10)`


## Some code

```{r}
head(mtcars)
```



## Some code ECHO and COMMENT

```{r, echo=TRUE, comment=""}
head(mtcars)
```

Echo di default è False, non pubblica il codice nelle slide.

Comment di default è ##  
Viene eliminato mettendo =""

## Some code EVAL

```{r, eval=FALSE}
head(mtcars)
```

Con EVAL=FALSE, Knitr non lancia il codice. Il chunk funziona in Markdown per testarlo

## Some plot

```{r, echo=FALSE, fig.align='center',fig.cap='My Figure Caption'}
plot(mtcars$wt, mtcars$mpg, xlab="Weight", ylab="Mpg")
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

